--- 
title: "A Model selection approach for Variable selection with censored data (R code) - Importance Sampling" 
author: "María Eugenia Castellanos, Gonzalo García Donato and Stefano Cabras" 
output: md_document 
--- 

  

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 
```


# Intro 

This code implements the importance sampling approach to obtain marginals and hence Bayes Factors. 

This does not implement stochastic model space exploration and all possible models ($2^k$, where $k$ is the number of covariates) are visited. 

# Data 

We consider the heart transplant survival dataset and two spurious uncorrelated variables. This is just one draw for the simulation study described in the paper. 

```{r,message=FALSE} 
rm(list=ls()) 
set.seed(17) 
library(compiler) 
library(mvtnorm) 
library(plyr) 
library(doParallel) 
source("library-bf-cens-conv-prior.R") 
source("library-bf-cens-conv-prior-2.R") 
library(survival) 
data(heart) 
jasa=jasa[jasa$transplant==1,] 
surv.time=jasa$fu.date-jasa$accept.dt
fecha.fin=as.Date(0, origin = "1974-04-01") 
cens.time=fecha.fin-jasa$accept.dt  
cens.time[jasa$fustat==0]=surv.time[jasa$fustat==0] 
dat.heart=data.frame(as.numeric(surv.time),as.numeric(jasa$fustat),as.numeric(cens.time),jasa$age,rnorm(nrow(jasa)),rnorm(nrow(jasa))) 
colnames(dat.heart)=c("survival","rel","cens","age","spur1","spur2") 
dat.heart=dat.heart[dat.heart$survival>0,] 
summary(dat.heart)
``` 

# Analysis 

## The null model 
Data for the null model are
```{r} 
data0=as.matrix(cbind(log(dat.heart$survival),dat.heart$rel,1))
``` 

IS approximation for the marginal

```{r}
tt0=optim(par=c(0,0),fn=log.post.lnormal,control=list(fnscale=-1),Data=data0,method=optimmethod,hessian=TRUE)
var.prop=-solve(tt0$hessian)

nsimul=10000
parms.hat0=tt0$par
res=post(log.post.lnormal,nsimul=nsimul,parms.init=parms.hat0,dat=data0)
res$par=res$par[-(1:(nsimul*0.3)),]
mu.prop=apply(res$par,2,mean)
Sigma.prop=cov(res$par)
nsim=40000
thetas=rmvt(nsim, delta = mu.prop, sigma = Sigma.prop,df=3)

lnum=apply(thetas,1,log.post.lnormal.0.our,Data=data0)
lden=apply(thetas,1,dmvt,delta=mu.prop, sigma =Sigma.prop,df=3,log=TRUE)

(lm0=log(mean(exp(lnum-lden))))
``` 

## Rest of the models 

The rest of models is defined upon the full matrix. All models will be examined (no random search). 

```{r} 
var.name=c("age","spur1","spur2") 
k=length(var.name)
n=nrow(dat.heart)
Xfull=dat.heart[,var.name]
Xfull=scale(Xfull) 
colnames(Xfull)=var.name 
Xfull=as.data.frame(Xfull) 
mod.list=index.models(ncol(Xfull)) 
nmodels=length(mod.list) 
``` 

Parallel calculation: 
```{r}
cl <- makePSOCKcluster(4) 
registerDoParallel(cl) 
```

These are the examined models: 

```{r} 
llply(mod.list,function(x) colnames(Xfull)[x]) 
```

We have `r nmodels` models more than the null, whose marginals are approximated with IS with $g$ is integrated over the robust prior (uncomment `r #robust#`) or inverse Gamma (uncomment `r #ig#`) or fixed (uncomment `r #gfixed#`) with this code.

```{r,cache=TRUE} 
lm1 <- foreach(i=1:nmodels, .combine=c) %dopar% { 
    source("library-bf-cens-conv-prior.R") 
    source("library-bf-cens-conv-prior-2.R")
    library(mvtnorm)
    #robust# marg1.allpara.robust(y=log(dat.heart$survival),rel=dat.heart$rel,ct=log(dat.heart$cens),X=Xfull[mod.list[[i]]],k.star=0,nsim.marg = 10000,nsim.post = 5000)$marg
 #ig#
  marg1.allpara.igamma(y=log(dat.heart$survival),rel=dat.heart$rel,cens=log(dat.heart$cens),X=Xfull[mod.list[[i]]],k.star=0,nsim.marg = 10000,nsim.post = 5000)$marg 
  #gfixed#  marg1.allpara.gfixed(y=log(dat.heart$survival),rel=dat.heart$rel,cens=log(dat.heart$cens),X=Xfull[mod.list[[i]]],k.star=0,nsim.marg = 10000,nsim.post = 5000)$marg
}
stopCluster(cl)
lm1=log(lm1)
``` 

# BF, model posterior probabilities and posterior inclusion probabilities 

## BFs and model posterior probabilities 

```{r} 
mdim=unlist(lapply(mod.list,function(x) length(x))) 
norm.mdim=table(mdim) 
mod.prior=1/norm.mdim[mdim] 
mod.prior=c(mod.prior,1) 
mod.prior=mod.prior/sum(mod.prior) 
BF=exp(lm1-lm0) 
mod.pp=prob.post(BF,mod.list,scott=TRUE) 
```

A matrix with the summary: 

```{r} 
results<- matrix(0, ncol=ncol(Xfull)+4, nrow=nmodels+1) 
colnames(results)<- c(colnames(Xfull), "marg", "BF", "PriorProb", "PosteriorProb") 
for (i in 1:nmodels){ 
  results[i,mod.list[[i]]]<- 1 
  results[i,ncol(Xfull)+(1:2)]<- c(lm1[i],BF[i]) 
  results[i,ncol(Xfull)+3]<- mod.prior[i] 
}
results[nmodels+1,ncol(Xfull)+(1:3)]<- c(lm0, 1,mod.prior[nmodels+1]) 
results[,"PosteriorProb"]<- c(mod.pp[-1],mod.pp[1]) 
rownames(results)=c(paste("Model ",1:nmodels),"Null Model") 
results 
``` 

## High posterior model 


```{r} 
hpm=order(results[,"PosteriorProb"],decreasing = TRUE)[1] 
rownames(results)[hpm] 
``` 

## Posterior inclusion probabilities and median probability model 

```{r} 
(pip=colSums(t(t(results[,1:ncol(Xfull)]*results[,"PosteriorProb"])))) 
mpm=(pip>0.5)*1 
mpm=apply(results[,1:k],1,function(x) all(x==mpm)) 
rownames(results)[mpm] 
```
