--- 

title: "A Model selection approach for Variable selection with censored data (R code)" 

author: "María Eugenia Castellanos, Gonzalo García Donato and Stefano Cabras" 

output: html_document 

--- 

  

```{r setup, include=FALSE} 

knitr::opts_chunk$set(echo = TRUE) 

``` 

  

# Intro 

  

  

This code implements, for each entertained model $\Sigma^M_\gamma(\hat\beta_0,\hat\sigma)$ as the prior covariance matrix, where the point estimators are the posterior means of the corresponding parameters under the null model.  

  

Moreover, all marginals are approximated with Laplace. 

  

This does not implement stochastic model space exploration and all possible models ($2^k$, where $k$ is the number of covariates) are visited. 

  

# Data 

We consider the heart transplant survival dataset and two spurious uncorrelated variable. This is just one draw for the simulation study described in the paper. 

  

```{r,message=FALSE} 

rm(list=ls()) 

set.seed(17) 

library(compiler) 

library(mvtnorm) 

library(plyr) 

library(doParallel) 

source("library-bf-cens-conv-prior.R") 

source("library-bf-cens-conv-prior-2.R") 

library(survival) 

data(heart) 

#Seleccionamos solo los pacientes que han recibido trasplante 

jasa=jasa[jasa$transplant==1,] 

#El tiempo de seguimiento es: 

surv.time=jasa$fu.date-jasa$accept.dt   

#La fecha a la que se finaliza el estudio es: 

fecha.fin=as.Date(0, origin = "1974-04-01") 

cens.time=fecha.fin-jasa$accept.dt  

#Para los censurados, nos aseguramos de definir bien el tiempo de supervivencia 

cens.time[jasa$fustat==0]=surv.time[jasa$fustat==0] 

#Usando edad: 

dat.heart=data.frame(as.numeric(surv.time),as.numeric(jasa$fustat),as.numeric(cens.time),jasa$age,rnorm(nrow(jasa)),rnorm(nrow(jasa))) 

colnames(dat.heart)=c("survival","rel","cens","age","spur1","spur2") 

  

dat.heart=dat.heart[dat.heart$survival>0,] 

summary(dat.heart) 

``` 

  

# Analysis 

  

## The null model 

  

Data for the null model is 

```{r} 

data0=as.matrix(cbind(log(dat.heart$survival),dat.heart$rel,1)) 

``` 

  

Laplace approximation for the marginal of the null model and calcualtion of $\Sigma^M_\gamma(\hat\beta_0,\hat\sigma)$: 

  

```{r} 

tt0=optim(par=c(0,0),fn=log.post.lnormal,control=list(fnscale=-1),Data=data0,method=optimmethod,hessian=TRUE) 

var.prop=-solve(tt0$hessian) 

  

parms.hat0=tt0$par 

beta0.hat=parms.hat0[2] 

lsigma.hat=parms.hat0[1] 

  

hessi0=-tt0$hessian 

map.coef=as.vector(tt0$par) 

p=dim(hessi0)[1] 

  

lm0=log.post.lnormal(parms=map.coef,Data=data0)+p/2*log(2*pi)-0.5*log(det(hessi0)) 

``` 

  

## Rest of the models 

  

The rest of the models is defined upon the full matrix. All models will be examined (no random search). 

  

  

```{r} 

var.name=c("age","spur1","spur2") 

k=length(var.name) 

n=nrow(dat.heart) 

Xfull=dat.heart[,var.name] 

#Centramos la matriz X.full: 

Xfull=scale(Xfull) 

colnames(Xfull)=var.name 

Xfull=as.data.frame(Xfull) 

mod.list=index.models(ncol(Xfull)) 

nmodels=length(mod.list) 

``` 

  

If parallel calculation is needed, please uncomment this: 

  

```{r} 

cl <- makePSOCKcluster(4) 

registerDoParallel(cl) 

``` 

  

  

These are the examined models: 

  

```{r} 

llply(mod.list,function(x) colnames(Xfull)[x]) 

``` 

  

  

We have `r nmodels` models more than the null, whose marginals are approximated with Laplace with this code. 

  

```{r} 

lm1 <- foreach(i=1:nmodels, .combine=c) %dopar% { 

    source("library-bf-cens-conv-prior.R") 

    source("library-bf-cens-conv-prior-2.R") 

    marg1.allpara.gfixed.laplace(y=log(dat.heart$survival), 

                                rel=dat.heart$rel,ct=log(dat.heart$cens), 

                                X=as.matrix(Xfull[mod.list[[i]]]), 

                                k.star=0,nsim.marg = NULL, 

                                nsim.post = NULL,beta0.hat,lsigma.hat)$marg 

} 

``` 

  

# BF, model posterior probabilities and posterior inclusion probabilities 

  

## BFs and model posterior probabilities 

  

```{r} 

mdim=unlist(lapply(mod.list,function(x) length(x))) 

norm.mdim=table(mdim) 

mod.prior=1/norm.mdim[mdim] 

mod.prior=c(mod.prior,1) 

mod.prior=mod.prior/sum(mod.prior) 

BF=exp(lm1-lm0) 

mod.pp=prob.post(BF,mod.list,scott=TRUE) 

#A matrix with the summary: 

results<- matrix(0, ncol=ncol(Xfull)+4, nrow=nmodels+1) 

colnames(results)<- c(colnames(Xfull), "marg", "BF", "PriorProb", "PosteriorProb") 

for (i in 1:nmodels){ 

  results[i,mod.list[[i]]]<- 1 

  results[i,ncol(Xfull)+(1:2)]<- c(lm1[i],BF[i]) 

  results[i,ncol(Xfull)+3]<- mod.prior[i] 

} 

results[nmodels+1,ncol(Xfull)+(1:3)]<- c(lm0, 1,mod.prior[nmodels+1]) 

results[,"PosteriorProb"]<- c(mod.pp[-1],mod.pp[1]) 

rownames(results)=c(paste("Model ",1:nmodels),"Null Model") 

results 

``` 

  

## High posterior model 

  

```{r} 

hpm=order(results[,"PosteriorProb"],decreasing = TRUE)[1] 

rownames(results)[hpm] 

``` 

  

  

## Posterior inclusion probabilities and median probability model 

  

```{r} 

(pip=colSums(t(t(results[,1:ncol(Xfull)]*results[,"PosteriorProb"])))) 

mpm=(pip>0.5)*1 

mpm=apply(results[,1:k],1,function(x) all(x==mpm)) 

rownames(results)[mpm] 

``` 

  

 

 