--- 
title: "A Model selection approach for Variable selection with censored data (R code) - test-based Bayes factors (TBF)" 
author: "María Eugenia Castellanos, Gonzalo García Donato and Stefano Cabras" 
output: md_document
bibliography: references-articles.bib
--- 

  

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 
```


# Intro 

This code implements, the analysis with test-based Bayes factors (TBF) originally proposed by @Jo08 and @HuJo09 later revisited by @Heldetal15, 

This does not implement stochastic model space exploration and all possible models ($2^k$, where $k$ is the number of covariates) are visited. 

# Data 

We consider the heart transplant survival dataset and two spurious uncorrelated variable. This is just one draw for the simulation study described in the paper. 

```{r,message=FALSE} 
rm(list=ls()) 
set.seed(17) 
library(compiler) 
library(mvtnorm) 
library(plyr) 
library(doParallel) 
source("library-bf-cens-conv-prior.R") 
source("library-bf-cens-conv-prior-2.R") 
library(survival) 
data(heart) 
jasa=jasa[jasa$transplant==1,] 
surv.time=jasa$fu.date-jasa$accept.dt
fecha.fin=as.Date(0, origin = "1974-04-01") 
cens.time=fecha.fin-jasa$accept.dt  
cens.time[jasa$fustat==0]=surv.time[jasa$fustat==0] 
dat.heart=data.frame(as.numeric(surv.time),as.numeric(jasa$fustat),as.numeric(cens.time),jasa$age,rnorm(nrow(jasa)),rnorm(nrow(jasa))) 
colnames(dat.heart)=c("survival","rel","cens","age","spur1","spur2") 
dat.heart=dat.heart[dat.heart$survival>0,] 
summary(dat.heart)
``` 

# Analysis 

## Posterior inclusion probabilities based on TBF

The full matrix is 

```{r} 
var.name=c("age","spur1","spur2") 
k=length(var.name)
n=nrow(dat.heart)
Xfull=dat.heart[,var.name]
Xfull=scale(Xfull)
colnames(Xfull)=var.name 
Xfull=as.data.frame(Xfull) 
mod.list=index.models(ncol(Xfull)) 
nmodels=length(mod.list) 
``` 


These are the examined models: 

```{r} 
llply(mod.list,function(x) colnames(Xfull)[x]) 
```

These are the inclusion probabilities according to different versions of the TBF:

```{r}
source("TBFfunctions.R")
ipTBF(Xfull, y=dat.heart$survival, delta=dat.heart$rel, g.param="EB")
ipTBF(Xfull, y=dat.heart$survival, delta=dat.heart$rel, g.param="g=nu")
ipTBF(Xfull, y=dat.heart$survival, delta=dat.heart$rel, g.param="g=n")
ZSadapt.ipTBF(Xfull, y=dat.heart$survival, delta=dat.heart$rel)	
```

# References